Interval Probability for Fuzzy Quantum Theories

### 2016-05-12 prob.tex
prob.tex \section{Quantum Probability Spaces} verifying source...

\begin{definition}[Projection Operators; Orthogonality~\cite{BirkhoffVonNeumann1936,10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
a question~\cite{10.2307/2308516}, or an elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator
$P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection.
\item For any vector $\ket{\psi}\in \Hilb$,
  $\frac{\proj{\psi}}{\ip{\psi}{\psi}}$ is a projection.
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
  P_2$ is also a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1 + P_2$ will project onto the
  linear span of $S_1$ and $S_2$, i.e., $\left\{\ket{\psi_1} + \ket{\psi_2}
  \middle| \ket{\psi_1}\in S_1 \textrm{ and } \ket{\psi_2}\in S_2 \right\}$.
\end{itemize}
\end{definition}

@@

\begin{definition}[Commutativity~\cite{Redhead1987-REDINA,peres1995quantum,Swart2013}]
Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
  P_2P_1$;
If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
  a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1P_2$ will project onto the
  intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
\end{definition}

@@

\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,DBLP:journals/corr/abs-0910-2393,Maassen2010}]
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
    possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item The set of events consists of all projections. This set includes
  the empty projection, projection operators $\proj{\psi}$ for each
  state $\ket{\psi}$, sums of \emph{orthogonal} projections, and
  products of \emph{commuting} projections; 
\item $\mu(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $E_i$, we have
  $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$.
\end{itemize}
\qed\end{definition}

>>>>

\begin{definition}[Projection Operators; Orthogonality~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
a question~\cite{10.2307/2308516,DBLP:journals/corr/abs-0910-2393}, or an
elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection.
\item For any vector $\ket{\psi}\in \Hilb$,
  $\frac{\proj{\psi}}{\ip{\psi}{\psi}}$ is a projection.
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
  P_2$ is also a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1 + P_2$ will project onto the
  linear span of $S_1$ and $S_2$, i.e., $\left\{\ket{\psi_1} + \ket{\psi_2}
  \middle| \ket{\psi_1}\in S_1 \textrm{ and } \ket{\psi_2}\in S_2 \right\}$.
\end{itemize}
\end{definition}

@@

\begin{definition}[Commutativity~\cite{peres1995quantum}]
Projection operators $P_1$ and $P_2$ commute if $P_1P_2 =
  P_2P_1$;
If the projections $P_1$ and $P_2$ commute then $P_1P_2$ is also
  a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1P_2$ will project onto the
  intersection of $S_1$ and $S_2$, i.e., $S_1 \cap S_2$.
\end{definition}

@@

\begin{definition}[Quantum Probability Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\mu : \events \rightarrow [0,1]$ such that:\footnote {It is
    possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item The set of events consists of all projections. This set includes
  the empty projection, projection operators $\proj{\psi}$ for each
  state $\ket{\psi}$, sums of \emph{orthogonal} projections, and
  products of \emph{commuting} projections; 
\item $\mu(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $E_i$, we have
  $\mu\left(\sum_{i}E_{i}\right)=\sum_{i}\mu\left(E_{i}\right)$.
\end{itemize}
\qed\end{definition}
